Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-01-29 stp/paper_aaai/main.tex
start shortenning it

\usepackage{colortbl}
\usepackage{color}
\usepackage{xcolor}
\definecolor{Gray}{gray}{0.96}
\usepackage{algorithm}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algpseudocode}
\algrenewcommand\algorithmiccomment[2][\footnotesize]{{#1\hfill\(\triangleright\)
 #2}} %\normalsize
\usepackage{amssymb}
\usepackage{textcomp}

@@

@@

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Submission 1204)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Submission 1204}
\maketitle
\begin{abstract}
The problem of integrating heterogeneous data sources into an ontology is of high 
relevance in the database field. Several techniques exist to approach this 
problem. Nonetheless, side constraints on the data integration cannot be easily 
integrated with these tools and thus the results may be inconsistent. We 
present a new approach that combines Machine Learning and 
Constraint Programming techniques, by modeling the data integration problem as 
a Steiner Tree Problem in a weighted graph. We show that through this approach 
we can achieve better precision, recall and speed compared to state-of-the-art 
approaches. We provide a comprehensive set of experiments supporting our 
findings.
\end{abstract}

@@

Firstly, we build a graph which includes attributes (i.e. columns) from the new
source as well as ontology classes and properties.
We name it \emph{integration graph}.
It uses information gathered from the previously mapped data sources, and is further extended with information derived from the ontology.
%Firstly, we build a \emph{integration graph} which includes the 
%attributes from the new source as well as ontology classes and properties.
Secondly, we apply machine learning techniques to 
assign costs to its edges. 
Lastly, we use CP to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting 
Steiner Tree is a valid and coherent semantic model for the new source. 
Our contributions are:
\begin{itemize}
	\item A novel modeling framework for the \relonto{} problem which 
	seamlessly incorporates techniques from the areas of machine learning, knowledge representation and constraint programming.
%	\npr{symbolic AI, ontological reasoning, transitive closure}
	\item An efficient approach to handle attributes which cannot be matched to 
	the ontology, through a new semantic labeling model and a new STP 
	model with additional nodes in the integration graph.
	\item A flexible and extensible approach to the problem, which is easy to 
	reuse and adapt to specific situations. This is achieved since CP allows introduction of additional constraints with no changes to the solver. 
\end{itemize}

Section \ref{SEC:problem} formally states the problem. 
In Section \ref{SEC:ML} we present how we convert learnt data into a 
useful data representation. 
Section \ref{SEC:STP} shows how we model the problem as a STP, 
whereas Section \ref{SEC:CP} presents our implementation in CP. 
Section \ref{SEC:Res} shows the results. 
Section \ref{SEC:pw} compares with the previous work done to achieve this task.

@@

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class] (pe) at (0,0)  {Person};
	\node[class] (co) at (0,-2) {Organisation};
	\node[class] (ev) at (3,0.2) {Event};
	\node[class] (pl) at (5,-1) {Place};
	\node[class] (ci) at (3,-2.5) {City};
	\node[class] (st) at (5,-2.5) {State};

@@

\end{tikzpicture}
\caption{Example of ontology
(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has an object property'', 
`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has a data property'' and 
`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``subClassOf'' ). Example by
\protect\citeasnoun{Taheriyan2013}.
}
\label{FIG:onto}
\vspace{-3mm}
\end{figure}

@@

\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale=0.95]
\begin{scope}
	\node[class] (pe) at (3,0)  {\small Person1};
	\node[class] (co) at (6,0) {\small Org.1};
	\node[class] (ci) at (1,0) {\small City1};
	\node[class] (st) at (-1,0) {\small State1};

@@

\end{scope}
\end{tikzpicture}
\caption{Examples of two semantic models (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
{};}' are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
nodes).}
\label{FIG:sem}
\vspace{-3mm}
\end{figure}

@@

\subsection{Semantic Labeling}
The semantic types $\mathcal{L_O} = \{l_1, l_2, ..., l_p\}$ of an ontology 
correspond to all pairs $(c,d)$, where $c$ is a Class in $\mathcal{O}$, and $d$ 
is a data property of that class (including inherited properties). 
For example, from the ontology in Fig. \ref{FIG:onto}, we would get
(City,name) and (State,name).

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
Typically semantic labeling techniques encounter several problems.
Firstly, there can be naming conflicts~\cite{Pinkel:rodi}, including those 
cases where users represent the same data in different ways.
Secondly, semantically different attributes might have syntactically similar 
content, for example, startDate versus endDate for the Event class.
Thirdly, there may be a considerable number of attributes which do not have any 
corresponding property in the ontology, either by accident or deliberately.
%\ddg{CHECK!}

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $\Delta_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes, among others, characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column. 
A full list can be found in Appendix \ref{Ann:SemLab}.
%\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy.
% of the attribute's concatenated rows
Shannon's entropy 
%(or information entropy~\cite{Manning:Introduction})
 of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary.
%of all possible characters
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works by ~\citeasnoun{Pham:semantic} or~\citeasnoun{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

To provide an integrated view over the known source descriptions $\Delta_T$, we 
need to align their semantic models as well as all considered semantic 
types. 
This is achieved by constructing an \emph{alignment graph}.

The alignment graph is a directed weighted graph $\mathcal{G_O} = 
(\mathcal{V_O},\mathcal{E_O})$ built on top 
of the known semantic models and expanded using the semantic types 
$\mathcal{L_O}$ and the ontology $\mathcal{O}$. 
Similar to a semantic 
model, $\mathcal{G_O}$ contains both class and data nodes.
The links correspond 
to properties in  $\mathcal{O}$ and are weighted \cite{taheriyan2016learning}.

The algorithm we use to construct the alignment graph 
$\mathcal{G_O}$ was given by~\citeasnoun{taheriyan2016learning}.
Briefly, it has three parts:
%\begin{enumerate}
$(i)$ %\item 
adding the known semantic models,
$(ii)$ %\item 
adding the semantic types learned for the target source,
%\item 
$(iii)$ expanding the graph using the domain ontology.
%\end{enumerate}

@@

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ such that edges which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology.
In the next section we will see that this makes edges from semantic models 
more attractive. 
\citeasnoun{taheriyan2016learning} provide details on the weighting function.
%\ddg{How exactly are they weighted?}

An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
%Bigger examples can be found in \cite{Taheriyan2013}. 
Black links correspond to the links which are supported by the known semantic models. 
Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange 
ones correspond to the ones added to connect Classes of the ontology that never 
appeared in the semantic models).
% and can be assigned the 
%maximum weight $w_max$ \ddg{where does this weight come from?}

\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale=0.9]

@@

	\node[class,orange,fill=orange!30!white,text=black] (PL) at (3,\ysh/2)  
	{\small 
	Place1};

	\path[draw,hasaC,->,orange!30!white] (pe1) edge[bend left=10] (PL);
	\path[draw,hasaC,->,orange!30!white] (pe1) edge[bend left=-10] (PL);

	\path[draw,hasaC,->,orange!30!white] (pe2) edge[bend left=10] (PL);
	\path[draw,hasaC,->,orange!30!white] (pe2) edge[bend left=-10] (PL);

	\path[draw,hasaC,->,orange!30!white] (co1) edge[bend left=0] (PL);
	\path[draw,hasaC,->,orange!30!white] (co2) edge[out=45,in=225] (PL);

	\path[draw,hasaC,->,orange!30!white] (ev2) edge[out=90,in=0] (PL);

	\path[draw,isa,->,orange!30!white] (ci1) edge[out=-25,in=130] (PL);
	\path[draw,isa,->,orange!30!white] (pl2) edge[out=50,in=180] (PL);
	\path[draw,isa,->,orange!30!white] (st1) edge[out=-45,in=160] (PL);

\end{tikzpicture}
\caption{Example of alignment graph (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
{};}' `\protect\tikz{ \protect\node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
(0,0)  
{};}' are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\vspace{-3mm}
\end{figure}

@@

Certain patterns of connections can be prevalent in the domain.
For example, in Fig.~\ref{FIG:sem} both semantic models have class nodes ``City'', ``Organization'' and ``Person''.
According to the ontology in Fig.~\ref{FIG:onto} there are multiple ways to connect these nodes.
However, if we know that the ``Person'' works for the ``Organization'', then based on the known semantic models (Fig.~\ref{FIG:sem}), ``City'' is more likely to be the birth place of the ``Person'' rather than the location of the ``Organization''.
To increase the coherence of the generated semantic models, we would like to discover such patterns of connections.

%As an extension to the problem, we consider using pattern mining techniques in order to identify patterns in the training set of semantic model that repeat themselves often. 
%The hope is that with such information we can encourage the semantic model $m^\star$ for the new source to use groups of edges that                                       appeared often together in training semantic models.

%\npr{reformulate for typed directed multigraphs and example based on Fig3}
In our context, patterns are typed directed graphs.
We mine these patterns from the set of semantic models in the training set $\Delta_T$.
This is known as Transactional Frequent Graph Pattern Mining, which
includes the subgraph isomorphism problem, known to be NP-complete.
The frequency of a pattern is the number of semantic models 
which contain
at least one subgraph isomorphic to the pattern.
The \emph{support} of the pattern is calculated as its 
frequency relative to the number of semantic models.
This is an anti-monotonous measure, meaning that bigger 
patterns will have lower supports than their subgraphs.
% \ddg{Define support}
We solve the pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.  
We obtain patterns of size up to 6 in under 4 minutes for the biggest instances 
in our evaluation framework.
Hence, this pattern mining procedure is a highly 
scalable approach compared to the technique based on SPARQL queries 
from~\cite{Taheriyan:Leveraging}.
%\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
%cite my work on how databases perform for graph pattern matching. Should it be 
%better in related work?}

@@

\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale=0.9]
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
	Class nodes of Alignment Graph (i.e. $\mathcal{C_{G_O}}$)}};

@@

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
\end{tikzpicture}
\caption{Example of integration graph. (`\protect\tikz{ \protect\node[att] () at (0,0)  
{};}' are attribute nodes). We omit weights and only show the most likely 
matches for clarity. Data node
are the same as in Fig \ref{FIG:ali}.}
\label{FIG:inte}
\vspace{-3mm}
\end{figure}

Note that, although the alignment graph is directed, we disregard the
direction of edges for the STP model.
We disambiguate the direction and semantics of edges via their
weights.
We can further improve this step by using patterns.
%\npr{this was not completely correct}
%the semantic models are 
%not necessarily rooted graphs (e.g. Fig. \ref{FIG:sem}), therefore the 
%direction of the edges is ignored for the STP model (and are all treated as 
%undirected edges).

@@

\textbf{Patterns:}
As explained in Subsection \ref{SSEC:pattern-mining}, we also use 
graph patterns in order to incentivise the solution tree 
$T^\star$ to contain subgraphs of the alignment graph that have been frequently 
seen in the training set.
To do this, we use the support of each of the obtained patterns as a prize. If 
the tree contains a pattern, then its weight is automatically reduced by the 
value of the support of that pattern. We will see in the next section how this 
information is integrated in the model.

@@

\section{Modeling in Constraint Programming \label{SEC:CP}}
\subsection{Definitions}

@@

Constraint Programming (CP) allows the user to model a COP and give it 
to a solver that will find solutions while optimizing 
the objective function (and prove optimality).

Briefly, the way a CP solver works is by assigning a value to each variable of 
$\boldsymbol{v}$ in turn. 
\ignore{At each iteration it will check whether any 
constraint in $C$ is violated, in which case it will backtrack to change its 
last decision. \ignore{The choice of the order of the variables to be assigned, 
and the 
choice of the value to be assigned to each variable is called the \emph{search 
strategy}.}}
CP uses a combination of complete search and \emph{propagation}. The latter
removes inconsistent values 
from the domains of variables. That way, values that cannot appear in a 
solution, given the current set of decisions, are never tried by the search. 
\emph{Global constraints} are higher order constraints that enforce a 
complex 
constraint over a set of variables. They are implemented with 
specialized algorithms for performance.

\subsection{\relonto{} in Constraint Programming}
In order to model the \relonto{} problem we used the \minizinc{} language 
\cite{minizinc}, and the 
\chuffed{} solver \cite{chu2011improving} because it has a global constraint 
implemented for Steiner 
Tree Problems \cite{deuna2016steiner}. The model can be found in Appendix \ref{Ann:MZ}.

@@

Because there are global constraints in CP specialized in matching 
\cite{regin1994filtering}, we split the problem into two parts: the 
$\mathit{steiner}$ global constraint \cite{deuna2016steiner} will only deal with the part of the 
integration graph that corresponds to the alignment graph, and the 
$\mathit{alldifferent}$ global constraint will deal with the matching part of 
the problem.

@@

Note how this CP model is easy to adapt to more classic settings where no 
patterns are used (by dropping Eqs. \ref{EQ:patt} and \ref{EQ:pcost}), or 
without \emph{unknown} nodes (by dropping Eq. \ref{EQ:unk}).

We choose a search strategy that will first try to match attributes using the cheapest edges in $\mathcal{M}_\mathcal{O}^{s^\star}$. Then, it will try to use the cheapest unfixed edge $e\in\mathcal{E_O}$ that fills a pattern $p$ (i.e. $\forall e_p\in p, e_p \neq e, c_{e_p}$) such that $w_\mathcal{P}(p) > w_\mathcal{O}(e)$ or simply the cheapest edge if none fill a pattern.

@@

\subsection{Experimental Setup}

@@

\begin{figure}[!ht]\small
\centering
\begin{tikzpicture}[scale=0.39]
\pgfplotsset{
    scale only axis,
    xmin=0, xmax=9
}

>>>>

\usepackage{colortbl}
\usepackage{color}
\usepackage{xcolor}
\definecolor{Gray}{gray}{0.96}
\usepackage{algorithm}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algpseudocode}
\algrenewcommand\algorithmiccomment[2][\footnotesize]{{#1\hfill\(\triangleright\)
 #2}} %\normalsize
\usepackage{amssymb}
\usepackage{nicefrac}
\usepackage{textcomp}

@@

\newcommand{\forijcai}[1]{}

@@

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Submission 1228)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Submission 1228}
\maketitle
\begin{abstract}
The problem of integrating heterogeneous data sources into an ontology is of high 
relevance in the database field. Several techniques exist to approach this 
problem. Nonetheless, side constraints on the data integration cannot be easily 
integrated with these tools and thus the results may be inconsistent. We 
present a new approach that combines Machine Learning and 
Constraint Programming techniques, by modeling the data integration problem as 
a Steiner Tree Problem in a weighted graph. We show that through this approach 
we can achieve better precision, recall and speed compared to state-of-the-art 
approaches. We provide a comprehensive set of experiments backing our 
findings.
\end{abstract}

@@

Firstly, we build a graph which includes attributes (i.e. columns) from the new
source as well as ontology classes and properties.
We name it \emph{integration graph}.
It uses information gathered from the previously mapped data sources, and is further extended with information derived from the ontology.
%Firstly, we build a \emph{integration graph} which includes the 
%attributes from the new source as well as ontology classes and properties.
Secondly, we apply machine learning techniques to 
assign costs to its edges. 
Lastly, we use CP to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting 
Steiner Tree is a valid and coherent semantic model for the new source. 
Our contributions are:
%\begin{itemize}
	%\item 
	A novel modeling framework for the \relonto{} problem that use ML, KRR and CP techniques,
%	\npr{symbolic AI, ontological reasoning, transitive closure}
	%\item
	an efficient approach to handle attributes which cannot be matched to 
	the ontology, \forijcai{arg1, through a new semantic labeling model and a new STP 
	model with additional nodes in the integration graph.}
	%\item 
	a flexible and extensible approach to the problem, which is easy to 
	reuse and adapt to specific situations through the use of CP.\forijcai{ allows introduction of additional constraints with no changes to the solver.} 
%\end{itemize}

\forijcai{
Section \ref{SEC:problem} formally states the problem. 
In Section \ref{SEC:ML} we present how we convert learnt data into a 
useful data representation. 
Section \ref{SEC:STP} shows how we model the problem as a STP, 
whereas Section \ref{SEC:CP} presents our implementation in CP. 
Section \ref{SEC:Res} shows the results. 
Section \ref{SEC:pw} compares with the previous work done to achieve this task. 
}

@@

\begin{figure}[ht]
\centering
\scalebox{0.8}{
\begin{tikzpicture}
	\node[class] (pe) at (0,0)  {Person};
	\node[class] (co) at (0,-2) {Organisation};
	\node[class] (ev) at (3,0.2) {Event};
	\node[class] (pl) at (5,-1) {Place};
	\node[class] (ci) at (3,-2.5) {City};
	\node[class] (st) at (5,-2.5) {State};

@@

\end{tikzpicture}
}
\caption{Example of ontology
(`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\protect\tikz{ \protect\path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has an object property'', 
`\protect\tikz{ \protect\path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has a data property'' and 
`\protect\tikz{ \protect\path[isa,->] (0,1) -- (3ex,1);}' means ``subClassOf'' ). Example by
\protect\citeasnoun{Taheriyan2013}.
}
\label{FIG:onto}
\vspace{-3mm}
\end{figure}

@@

\begin{figure}[ht]
\centering\scalebox{0.8}{
\begin{tikzpicture}[scale=0.95]
\begin{scope}
	\node[class] (pe) at (3,0)  {\small Person1};
	\node[class] (co) at (6,0) {\small Org.1};
	\node[class] (ci) at (1,0) {\small City1};
	\node[class] (st) at (-1,0) {\small State1};

@@

\end{scope}
\end{tikzpicture}
}
\caption{Examples of two semantic models (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
{};}' are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
nodes).}
\label{FIG:sem}
\vspace{-3mm}
\end{figure}

@@

\subsection{Semantic Labeling}
The semantic types $\mathcal{L_O} = \{l_1, l_2, ..., l_p\}$ of an ontology 
correspond to all pairs $(c,d)$, where $c$ is a Class in $\mathcal{O}$, and $d$ 
is a data property of that class (including inherited properties). 
For example, in Fig. \ref{FIG:onto}, we would get
(City,name) and (State,name).

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
Typically semantic labeling techniques encounter several problems such as:
naming conflicts~\cite{Pinkel:rodi}, multiple data representations, and semantically different attributes might have syntactically similar 
content.%, for example, startDate versus endDate for the Event class.
Also, there may be a considerable number of attributes which have no 
corresponding property in the ontology (accidentaly or deliberately).
%\ddg{CHECK!}

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $\Delta_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes, among others, characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column. 
\forijcai{A full list can be found in Appendix \ref{Ann:SemLab}.}
%\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy.
% of the attribute's concatenated rows
Shannon's entropy 
%(or information entropy~\cite{Manning:Introduction})
 of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary.
%of all possible characters
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works by ~\citeasnoun{Pham:semantic} or~\citeasnoun{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

To provide an integrated view over the known source descriptions $\Delta_T$, we 
align their semantic models as well as all considered semantic 
types. 
This is achieved by constructing an \emph{alignment graph}.

The alignment graph is a directed weighted graph $\mathcal{G_O} = 
(\mathcal{V_O},\mathcal{E_O})$ built on top 
of the known semantic models and expanded using the semantic types 
$\mathcal{L_O}$ and the ontology $\mathcal{O}$. 
Similar to a semantic 
model, $\mathcal{G_O}$ contains both class and data nodes.
The links correspond 
to properties in  $\mathcal{O}$ and are weighted.
The full algorithm we use to construct the alignment graph 
$\mathcal{G_O}$ was given by~\citeasnoun{taheriyan2016learning}.
\forijcai{Briefly, it has three parts:
%\begin{enumerate}
$(i)$ %\item 
adding the known semantic models,
$(ii)$ %\item 
adding the semantic types learned for the target source,
%\item 
$(iii)$ expanding the graph using the domain ontology.
%\end{enumerate}
}

@@

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ such that edges which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology.
\forijcai{In the next section we will see that this makes edges from semantic models 
more attractive. }
\citeasnoun{taheriyan2016learning} provide details on the weighting function.
%\ddg{How exactly are they weighted?}
An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
%Bigger examples can be found in \cite{Taheriyan2013}. 
Black links are links supported by the known semantic models. 
Blue links are inferred from the ontology.\forijcai{(the orange 
ones correspond to the ones added to connect Classes of the ontology that never 
appeared in the semantic models).}
% and can be assigned the 
%maximum weight $w_max$ \ddg{where does this weight come from?}

\begin{figure}[ht]
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]

@@

	\node[class,text=black] (PL) at (3,\ysh/2)  
	{\small 
	Place1};

	\path[draw,hasaC,->,blue!70] (pe1) edge[bend left=10] (PL);
	\path[draw,hasaC,->,blue!70] (pe1) edge[bend left=-10] (PL);

	\path[draw,hasaC,->,blue!70] (pe2) edge[bend left=10] (PL);
	\path[draw,hasaC,->,blue!70] (pe2) edge[bend left=-10] (PL);

	\path[draw,hasaC,->,blue!70] (co1) edge[bend left=0] (PL);
	\path[draw,hasaC,->,blue!70] (co2) edge[out=45,in=225] (PL);

	\path[draw,hasaC,->,blue!70] (ev2) edge[out=90,in=0] (PL);

	\path[draw,isa,->,blue!70] (ci1) edge[out=-25,in=130] (PL);
	\path[draw,isa,->,blue!70] (pl2) edge[out=50,in=180] (PL);
	\path[draw,isa,->,blue!70] (st1) edge[out=-45,in=160] (PL);

\end{tikzpicture}}
\caption{Example of alignment graph (`\protect\tikz{ \protect\node[class, inner sep = 2] () at (0,0)  
{};}' \forijcai{`\protect\tikz{ \protect\node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
(0,0)  
{};}'} are class nodes, and `\protect\tikz{ \protect\node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\vspace{-3mm}
\end{figure}

@@

Certain patterns of connections can be prevalent in the domain.
\forijcai{
For example, in Fig.~\ref{FIG:sem} both semantic models have class nodes ``City'', ``Organization'' and ``Person''.
According to the ontology in Fig.~\ref{FIG:onto} there are multiple ways to connect these nodes.
}
If we know that the ``Person'' works for the ``Organization'', then based on the known semantic models (Fig.~\ref{FIG:sem}), ``City'' is more likely to be the birth place of the ``Person'' rather than the location of the ``Organization''.
To increase the coherence of the generated semantic models, we would like to discover such patterns of connections.
%As an extension to the problem, we consider using pattern mining techniques in order to identify patterns in the training set of semantic model that repeat themselves often. 
%The hope is that with such information we can encourage the semantic model $m^\star$ for the new source to use groups of edges that                                       appeared often together in training semantic models.

%\npr{reformulate for typed directed multigraphs and example based on Fig3}

%In our context, patterns are typed directed graphs.
We mine these patterns from the set of semantic models in the training set $\Delta_T$.
This is known as Transactional Frequent Graph Pattern Mining\forijcai{, which
includes the subgraph isomorphism problem, known to be NP-complete}.
The frequency of a pattern is the number of semantic models 
which contain
at least one subgraph isomorphic to the pattern.
The \emph{support} of the pattern is calculated as its 
frequency relative to the number of semantic models.
This is an anti-monotonous measure, meaning that bigger 
patterns will have lower supports than their subgraphs.
% \ddg{Define support}
We solve the pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs.\forijcai{and uses Apache Flink for scalability.}  
We obtain patterns of size up to 6 in under 4 minutes for the biggest instances 
in our evaluation framework.
Hence, this pattern mining procedure is a highly 
scalable approach compared to the technique based on SPARQL queries 
from~\cite{Taheriyan:Leveraging}.
%\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
%cite my work on how databases perform for graph pattern matching. Should it be 
%better in related work?}

@@

\begin{figure}[ht]
\centering \scalebox{0.8}{
\begin{tikzpicture}[scale=0.9]
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
	Class nodes of Alignment Graph (i.e. $\mathcal{C_{G_O}}$)}};

@@

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
\end{tikzpicture} }
\caption{Example of integration graph. (`\protect\tikz{ \protect\node[att] () at (0,0)  
{};}' are attribute nodes). We omit weights and only show the most likely 
matches for clarity. Data node
are the same as in Fig \ref{FIG:ali}.}
\label{FIG:inte}
\vspace{-3mm}
\end{figure}

Note that, although the alignment graph is directed, we disregard the
direction of edges for the STP model.
We disambiguate the direction \forijcai{and semantics} of edges via their
weights.
\forijcai{We can further improve this step by using patterns.}
%\npr{this was not completely correct}
%the semantic models are 
%not necessarily rooted graphs (e.g. Fig. \ref{FIG:sem}), therefore the 
%direction of the edges is ignored for the STP model (and are all treated as 
%undirected edges).

@@

\textbf{Patterns:}
As explained in Sec. \ref{SSEC:pattern-mining}, we use 
graph patterns to incentivise the solution tree 
$T^\star$ to contain subgraphs of the alignment graph that have been frequently 
seen in the training set.
To do this, we use the support of each obtained patterns as a prize. If 
the tree contains a pattern, then its weight is automatically reduced by the 
value of the support of that pattern. Sec. \ref{SEC:rel2ontocp} shows how this is integrated in the model.

@@

\section{Modeling in Constraint Programming \label{SEC:CP}}
%\subsection{Definitions}

@@

CP allows the user to model a COP and give it 
to a solver that will find solutions while optimizing 
the objective function (and prove optimality).

Briefly, a CP solver assigns values to each variable of 
$\boldsymbol{v}$ in turn. 
\ignore{At each iteration it will check whether any 
constraint in $C$ is violated, in which case it will backtrack to change its 
last decision. \ignore{The choice of the order of the variables to be assigned, 
and the 
choice of the value to be assigned to each variable is called the \emph{search 
strategy}.}}
CP uses a combination of complete search and \emph{propagation}. The latter
removes inconsistent values 
from the domains of variables. That way, values that cannot appear in a 
solution, given the current set of decisions, are never tried by the search. 
\emph{Global constraints} are higher order constraints that enforce a 
complex 
constraint over a set of variables. They are implemented with 
specialized algorithms for performance.

\subsection{\relonto{} in Constraint Programming\label{SEC:rel2ontocp}}
We used the \minizinc{} language 
\cite{minizinc}, and the 
\chuffed{} solver. \cite{chu2011improving}\forijcai{ because it has a global constraint 
implemented for Steiner 
Tree Problems \cite{deuna2016steiner}. The model can be found in Appendix \ref{Ann:MZ}}

@@

Since there are global constraints in CP specialized in matching 
\cite{regin1994filtering}, we split the problem into two parts: the 
$\mathit{steiner}$ global constraint \cite{deuna2016steiner} will only deal with the part of the 
integration graph that corresponds to the alignment graph, and the 
$\mathit{alldifferent}$ global constraint will deal with the matching part of 
the problem.

@@

\forijcai{
Note how this CP model is easy to adapt to more classic settings where no 
patterns are used (by dropping Eqs. \ref{EQ:patt} and \ref{EQ:pcost}), or 
without \emph{unknown} nodes (by dropping Eq. \ref{EQ:unk}).

We choose a search strategy that will first try to match attributes using the cheapest edges in $\mathcal{M}_\mathcal{O}^{s^\star}$. Then, it will try to use the cheapest unfixed edge $e\in\mathcal{E_O}$ that fills a pattern $p$ (i.e. $\forall e_p\in p, e_p \neq e, c_{e_p}$) such that $w_\mathcal{P}(p) > w_\mathcal{O}(e)$ or simply the cheapest edge if none fill a pattern.
}

@@

%\subsection{Experimental Setup}

@@

\begin{figure}[t]\small
\centering
\begin{tikzpicture}[scale=0.35]
\pgfplotsset{
    scale only axis,
    xmin=0, xmax=9
}
